`make.traits`

### 2023-03-27 inst/gitbook/02_make.traits.Rmd
What is a trait?

>>>>

> **What is a trait in biology?** This is one of these epistemological question like what _is_ a species that is not covered by all means in this package.
For the purpose of _this manual_, **biological trait** can be any coherent process of any number of dimensions which can or cannot be independent.
Basically anything can be a trait as well as it's defined by the user (e.g. one trait can be a 20 dimensional Brownian process that's correlated to a 1D OU process - which is another trait).
For the purpose of the syntax in _this package_ though, a **trait in `dads`** is a column in the output trait matrix.
For example, one might be interested in a biological trait that is "beak shape" which is defined as one complex biological trait that is the Procrustes superimposition of 4 3D landmarks and 300 3D semi-landmarks.
This single "beak shape" **biological trait** is then composed of 912 **traits in `dads`** (i.e. a matrix of $$(4+300)\times3$$ columns).
